climate_sites

### 2019-06-11 analysis/clima_real.Rmd
update

@@

```{r}
dendro_worldclim <- data.frame(
  coordinates(fw), 
  name = fw$name, 
  site = fw$site,
  loc = fw$loc, 
  prec = extract(prec_annual, fw),
  tavg = extract(tmean, fw)
)

dendro_worldclim <- dendro_worldclim %>% group_by(site) %>% summarise(p = mean(prec), t = mean(tavg))

@@

```{r}
sur <- s6246y %>% rbind(s6248y) %>% 
  dplyr::select(-n) %>% 
  group_by(year) %>% 
  summarise(prec_avg = mean(valor), 
            n = n())

@@

sur %>% ggplot(aes(y=prec_avg, x=year)) + geom_point(aes(size = n)) + geom_smooth()

@@

# Otras estaciones PSN

>>>>

tmin <- stack("/Users/ajpelu/Google Drive/my_repos/clima/data_raw/gridded/worldclim/v2/30sec/tmin/wc_tmin_SN_30sec.grd")
tmin_avg <- calc(tmin, mean)

tmax <- stack("/Users/ajpelu/Google Drive/my_repos/clima/data_raw/gridded/worldclim/v2/30sec/tmax/wc_tmax_SN_30sec.grd")

tmax_avg <- calc(tmax, mean)

@@

```{r}
dendro_worldclim <- data.frame(
  coordinates(fw), 
  name = fw$name, 
  site = fw$site,
  loc = fw$loc, 
  prec = raster::extract(prec_annual, fw),
  tavg = raster::extract(tmean, fw), 
  tmin = raster::extract(tmin_avg, fw),
  tmax = raster::extract(tmax_avg, fw)
)

dendro_worldclim <- dendro_worldclim %>% group_by(site) %>% summarise(p = mean(prec), t = mean(tavg), tmin = mean(tmin), tmax = mean(tmax))

@@

```{r}
# 42 prec 
# canar
psn <- read_csv(here::here("/data_raw/climate/datos_psn07_03.csv"))

psn07 <- psn %>% filter(cli_estacion_id == 11) %>% 
  filter(cli_variable_id == 42) %>% 
  group_by(year=floor_date(fecha, "year")) %>%
  summarise(valor = sum(valor), n=n())

```{r}
sur <- s6246y %>% rbind(s6248y, psn07) %>% 
  dplyr::select(-n) %>% group_by(year) %>% 
  summarise(prec_avg = mean(valor), 
            n = n())

@@

sur %>% ggplot(aes(y=prec_avg, x=year)) + geom_point(aes(size = n))

@@
